Scalar Items in Embedded Position: {A}nother Experimental Approach

### 2012-05-21 text/paper/paper.tex
paper sec com

\noindent If this upper-bounding inference would occur often and
systematically enough, then it may well be that also embedded
occurrences of \emph{some} get enriched, in some fashion or other, to
contribute \emph{in situ} the enriched meaning \emph{some but not
  all}. Indeed, even \citeauthor{Grice1975:Logic-and-Conve} envisaged
this possibility when he wrote: ``It may not be impossible for what
starts life, so to speak, as a conversational implicature to become
conventionalized'' \citep[p.58]{Grice1975:Logic-and-Conve}. But then
there are at least three relevant candidate readings for \as- and
\es-sentences: (i) a \emph{literal reading} like in
(\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
has only its literal meaning as in; (ii) a \emph{global reading} like
in (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where, according
to the Gricean intuition, we compare utterances of (\ref{bsp:AE}) or
(\ref{bsp:GE}) with utterances of the corresponding sentences
(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
\emph{some} is read to mean \emph{some but not all} in the scope of
the embedding quantifier.

@@

>>>>

\noindent If this upper-bounding inference would occur often and
systematically enough, then it may well be that also embedded
occurrences of \emph{some} get enriched, in some fashion or other, to
contribute \emph{in situ} the enriched meaning \emph{some but not
  all}. Indeed, even \citeauthor{Grice1975:Logic-and-Conve} envisaged
this possibility when he wrote: ``It may not be impossible for what
starts life, so to speak, as a conversational implicature to become
conventionalized'' \citep[p.58]{Grice1975:Logic-and-Conve}. But then
there are at least three relevant candidate readings for \as- and
\es-sentences (see Section~\ref{sec:get-know-your} for more detail and
some helpful illustrations): (i) a \emph{literal reading} like in
(\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
has only its literal meaning as in; (ii) a \emph{global reading} like
in (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where, according
to the Gricean intuition, we compare utterances of (\ref{bsp:AE}) or
(\ref{bsp:GE}) with utterances of the corresponding sentences
(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
\emph{some} is read to mean \emph{some but not all} in the scope of
the embedding quantifier.

@@

The main question we are interested in here is which of these three
conceivable readings is available to subjects na\"{i}ve to all
pragmatic theory. We are moreover interested in the more refined
question which of the available readings na\"{i}ve subjects prefer.

Addressing these issues empirically is highly relevant because they
lie at the heart of the current debate of the exact location and
nature of the interface between semantics and pragmatics. In rough
approximation, there are three camps ---more or less fiercely---
involved in this border war. (We will give a more detailed description
of the various theoretical positions below in
Section~\ref{sec:theories-predictions}.) Firstly, there are
\emph{pragmatic traditionalists} who seek to conserve the spirit of
\citeauthor{Grice1975:Logic-and-Conve}'s
(\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
possible
\citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}. Traditionalists
happily acknowledge the existence of global readings, but might
consider local readings either unavailable or a beast distinct from
scalar implicatures. Opposed to that is the camp of \emph{lexical
  conventionalists}
\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
who maintain a double lexical meaning for scalar \emph{some}, one as
in logical semantics, and one with the enriched meaning \emph{some but
  not all}. As the latter is considered a default, lexical
conventionalism has no problem accounting for local readings, and in
fact would consider these the preferred readings. Thirdly and finally,
there is also the ever more powerful camp of \emph{grammaticalists}
who defend that the distribution of upper-bounded readings of
\emph{some} is best explained by postulating a silent operator, akin
to the meaning of the particle \emph{only} \citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Sauerland2012:The-Computation}. This operator may be
applied in compositional semantics also in the scope of other logical
operators, so as to account for, e.g., local readings of \as- and
\es-sentences.
